Estimating the number of clusters using Cross Validation

### 2015-08-27 cvclust.tex
fix some typos

\begin{figure}[H]
\centering
\includegraphics[width=25pc]{demo/nullcorr/equal.pdf}
\caption{Cross-validation error on $10$ replicates, with the number of
clusters $k$ ranging from $1$ to $5$.  Data is generated from two-dimensional
multivariate normal distribution with correlation $\rho$.  The Gabriel
cross-validation criterion chooses the correct answer $k = 1$ whenever
$\rho < 0.5$; the criterion chooses $k = 2$ clusters whenever $|\rho| > 0.5$.}
\label{fig:nullcorr-equal}
\end{figure}

@@

Suppose that $\cov(Y) = U \Lambda U^\T$ is the eigendecomposition of
$\cov(Y)$. For simplicity, suppose that the leading eigenvalue $\lambda_1$
has unit multiplicity, so that the first principal subspace of $Y$ is a line,
given by the span of the vector $u_1 \in \R^q$. When we apply $k$-means to
$Y_1, \dotsc, Y_n$, the centroids will be close to
$\bmuY_1 =  \sqrt{2\lambda_1 /\pi} u_1$ and
$\bmuY_2 = -\sqrt{2\lambda_1 /\pi} u_1$, with errors of size $\OhP(n^{-1/2})$.

>>>>

\begin{figure}[H]
\centering
\includegraphics[width=25pc]{demo/nullcorr/equal.pdf}
\caption{Cross-validation error on $10$ replicates, with the number of
clusters $k$ ranging from $1$ to $5$.  Data is generated from two-dimensional
multivariate normal distribution with correlation $\rho$.  The Gabriel
cross-validation criterion chooses the correct answer $k = 1$ whenever
$|\rho| < 0.5$; the criterion chooses $k = 2$ clusters whenever $|\rho| > 0.5$.}
\label{fig:nullcorr-equal}
\end{figure}

@@

Suppose that $\cov(Y) = U \Lambda U^\T$ is the eigendecomposition of
$\cov(Y)$. For simplicity, suppose that the leading eigenvalue $\lambda_1$
has unit multiplicity, so that the first principal subspace of $Y$ is a line,
given by the span of the vector $u_1 \in \R^q$. When we apply $k$-means to
$Y_1, \dotsc, Y_n$ with $k = 2$, the centroids will be close to
$\bmuY_1 =  \sqrt{2\lambda_1 /\pi} u_1$ and
$\bmuY_2 = -\sqrt{2\lambda_1 /\pi} u_1$, with errors of size $\OhP(n^{-1/2})$.
